---
title: "Heart_Capstone"
output: 
  flexdashboard::flex_dashboard:
    orientation: columns
    vertical_layout: fill
runtime: shiny
---

```{r setup, include=FALSE}
library(flexdashboard)
library(tidyverse)
library(ggplot2)
library(reshape2)
library(dplyr)
library(leaflet)
library(plotly)
library(DT)
```
Heart Disease Data Analysis
=====================================  
 

Column {data-height = 4000 .tabset}
-----------------------------------------------------------------------
### Raw Data Display
```{r}
heart = read_csv("/Users/erinwang/ds4ph-bme/CapstoneProject/heart.csv")
htdf = select(heart,-"output")
datatable(htdf)
```
Column {data-width = 400}
-----------------------------------------------------------------------
### Variable Name Description

Description:
A data set contains variables related to heart disease of 303 object. The raw data is downloaded from kaggle.com which is a database website where data sets are publicly accessible for self investigation. A link can be find here. [link](https://www.kaggle.com/johnsmith88/heart-disease-dataset)


Variables:
<br>1. age
<br>2. sex
<br>3. chest pain tyep (4 values)
<br>4. resting blood pressure
<br>5. serum cholestoral level
<br>6. fasting blood sugar >120mg/dl
<br>7. resting electrocardiographic results (3 values)
<br>8. maximum heart rate achieved
<br>9. exercise induced angina
<br>10. oldpeak = ST depression induced by exercise relative to rest
<br>11. the slope of the peak exercise ST segmen
<br>12. number of major vessels (0-3) colored by flourosopy
<br>13. thal: 0 = normal; 1 = fixed defect; 2 = reversable defect


Column {data-width = 400}
-----------------------------------------------------------------------
### Heatmap representing correlation

```{r}
cormat <- round(cor(htdf),2)
melted_cormat <- melt(cormat)
g = ggplot(data = melted_cormat,aes(x = Var1, y = Var2, fill = value)) 
g + geom_tile()

```

  
Heart Disease Logistic Regression
=====================================  

```{r}

```

  
User Self Diagnosis
=====================================  

Column {.sidebar data-width = 200}
-----------------------------------------------------------------------

```{r}
numericInput("age", "Age", value = 0)

selectInput("sex", "Sex", choices = list("Male", "Female"), selected = "Male")

sliderInput("cp", "Chest Pain Type", min = 0, max = 3, value = 0, step = 1)

sliderInput("bps", "Resting Blood Pressure (mm Hg)", min = 90, max = 200, value = 120)

sliderInput("chol", "Serum Cholestoral (mg/dl)", min = 120, max = 600, value = 200)

checkboxInput("fbs", "Fasting Blood Sugar > 120mg/dl", value = FALSE)

sliderInput("thalach", "Maximum Heart Rate Achieved", min = 70, max = 210, value = 150)

checkboxInput("exang", "Exercise Induced Angina", value = FALSE)

```

Column {data-width=650}
-----------------------------------------------------------------------

### Chart A

```{r}

```

Column {data-width=350}
-----------------------------------------------------------------------

### Chart B

```{r}

```

### Chart C

```{r}

```

