---
title: "Heart_Capstone"
output: 
  flexdashboard::flex_dashboard:
    orientation: columns
    vertical_layout: fill
runtime: shiny
---

```{r setup, include=FALSE}
library(flexdashboard)
library(tidyverse)
library(ggplot2)
library(reshape2)
library(dplyr)
library(leaflet)
library(plotly)
library(DT)
library(glmnet)
library(caret)
```


Heart Disease Data Analysis
=====================================  

Column {data-height = 4000 .tabset}
-----------------------------------------------------------------------
### Raw Data Display

```{r}
heart = read_csv("https://raw.githubusercontent.com/Erinywang/ds4ph_Capstone/main/heart.csv") %>% 
    rename(rtbp = trtbps, rtecg = restecg) %>%
    mutate(sex = as.factor(sex), cp = as.factor(cp), fbs = as.logical(fbs)) 

htdf = select(heart,-"output")
datatable(htdf)

ht = select(heart, age, sex, cp, rtbp, chol, fbs, output)
dt = sort(sample(nrow(ht), nrow(ht)*.8))
ht_train = ht[dt,]
ht_test = ht[-dt,]
```

Column {data-width = 400}
-----------------------------------------------------------------------
### Variable Name Description

Description:
A data set contains variables related to heart disease of 303 object. The raw data is downloaded from kaggle.com which is a database website where data sets are publicly accessible for self investigation. A link can be find here. [link](https://www.kaggle.com/johnsmith88/heart-disease-dataset)


Variables:
<br>1. age
<br>2. sex
<br>3. chest pain type (4 values)
<br>4. resting blood pressure
<br>5. serum cholesterol level
<br>6. fasting blood sugar >120mg/dl
<br>7. resting electrocardiographic results (3 values)
<br>8. maximum heart rate achieved
<br>9. exercise induced angina
<br>10. oldpeak = ST depression induced by exercise relative to rest
<br>11. the slope of the peak exercise ST segmen
<br>12. number of major vessels (0-3) colored by fluoroscope
<br>13. thal: 0 = normal; 1 = fixed defect; 2 = reversible defect

Column {data-width = 400}
-----------------------------------------------------------------------
### Heatmap representing correlation

```{r}
cormat <- round(cor(htdf),2)
melted_cormat <- melt(cormat)
g = ggplot(data = melted_cormat,aes(x = Var1, y = Var2, fill = value)) 
g + geom_tile()

```

  
Heart Disease Logistic Regression
=====================================  

Column
-----------------------------------------------------------------------
### GLM

```{r}
fit = glm(formula = output ~ age + sex + cp + rtbp + chol + fbs,
          family = "binomial", data = ht_train)
summary(fit)

prob = predict(fit)

predict = rep(0, nrow(ht))
predict[prob > .5] = 1

conf_matrix = table(predicted_values = predict, actual_values = ht$output)

accuracy = mean(predict == ht$output)
sensitivity(conf_matrix)
specificity(conf_matrix)
```

Column
-----------------------------------------------------------------------
### Lasso

```{r}
x_train = model.matrix(output ~ age + sex + cp + rtbp + chol + fbs, data = ht_train)
y_train = ht_train$output

fit1 = cv.glmnet(x_train, y_train, alpha = 0.2, family = "binomial", type.measure = "mse")
plot(fit1)

lambda = fit1$lambda.1se
coef(fit1,s = lambda)


x_test = model.matrix(output ~ age + sex + cp + rtbp + chol + fbs, data = ht_test)
y_test = ht_test$output

prob1 = predict(fit1, newx = x_test, s = lambda, type = "response")

predict1 = rep(0, nrow(ht_test))
predict1[prob1 > .5] = 1

conf_matrix1 = table(predicted_values = predict1, actual_values = ht_test$output)

accuracy1 = mean(predict1 == ht_test$output)
sensitivity(conf_matrix1)
specificity(conf_matrix1)
```


  
User Self Diagnosis
=====================================  

Column {.sidebar data-width = 200}
-----------------------------------------------------------------------

```{r}

numericInput("age", "Age", value = 0)

selectInput("sex", "Sex", choices = list("Male", "Female"), selected = "Male")

sliderInput("cp", "Chest Pain Type", min = 0, max = 3, value = 0, step = 1)

sliderInput("bps", "Resting Blood Pressure (mm Hg)", min = 90, max = 200, value = 120)

sliderInput("chol", "Serum Cholestoral (mg/dl)", min = 120, max = 600, value = 200)

sliderInput("fbs", "Fasting Blood Sugar", min = 50, max = 200, value = 80)

```

Column {data-width=650}
-----------------------------------------------------------------------

### Chart A

```{r}

```

Column {data-width=350}
-----------------------------------------------------------------------

### Chart B

```{r}

```

### Chart C

```{r}

```

